Ensuring Fairness with Transparent Auditing of Ethical Bias in AI Systems\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-04-25 abstract.tex
added introduction

\section{Ease of Use}
fairness is subjective, based on culture and often not quantitative
for AI system we use quantitative fairness measures
transparency and objectivity example : COMPAS
third party needed for auditing example : propublica like entity can use our stuff; we're not replacing but supplement; domain knowledge
we propose a framework

>>>>

Cases such as COMPAS underscore the critical importance of rigorously examining the fairness of AI systems by third parties. Fairness is fundementally a subjective social construct, heavily influenced by cultural context and deeply rooted in historical inequalities.

We leverage quantitative measures that provide transparent and objective insights. By employing mathematically rigorous methodologies, our research can offer a more deeper look into the fairness of AI systems, enabling third parties to make more informed and robust judgment. For example, it would reveal that the COMPAS system violates a fairness measure called equalized odds.

In addition to equalized odds, there are a number of fairness measures for AI systems. Our framework aims to help third parties understand these metrics and navigate complex datasets with ease, pinpointing instances of bias and discrimination.

With our tool, a third party such as ProPublica could clearly and easily demonstrates that COMPAS violates equalized odds according to their datasets. Our platform empowers organizations to conduct thorough assessments of AI fairness and uncover discrepancies in predictive models.

This functionality not only facilitates sound judgment but also fosters objectivity and transparency regarding AI systems, ultimately bolster the claim of fairness and justice in AI-enabled decision-making.

Our tool is written in Python and is offered as a Python package. It supports common datasets format such as csv. It is open-sourced and publicly available for downloads.
